---
title: "scRNA-Seq Analysis"
subtitle: "Hands-On Excercises"
author: "Åsa Björklund"
date: "`r format(Sys.Date(),format='%d-%b-%Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: united
    highlight: tango
    df_print: paged
    code_folding: "none"
    self_contained: false
    keep_md: false
    encoding: "UTF-8"
    css: ["assets/course.css"]
---

```{r,echo=FALSE,message=FALSE,warning=FALSE,results='hide'}
# run setup code
source("assets/setup.R")
#knitr::opts_chunk$set(fig.height=4,fig.width=6)
```

```{r,echo=FALSE,results='hide'}
library(ggplot2)
library(dplyr)
```

<img src="assets/logo.svg" alt="logo_raukr" class="trlogo">

---

<p class="abstract">
This is the hands-on material for **single-cell RNASeq analyses**. These are series of excercises to help you get started with reproducible research using R. The code is hidden by default. Click on the 'Code' button on the right side to show the code. You can consult the R Markdown cheatsheet for quick reference.
</p>

---

# Introduction

<Some intro here to scRNA-Seq>

# Labs

## Seurat

Single-cell RNA-seq data workflow with Seurat including filtering, QC and clustering. Click [here](seurat_analysis.html).

## Scater

Single-cell RNA-seq data workflow and QC with Scater package. Click [here](scater_ilc.html).

## SC3

Single-cell RNA-seq concensus clustering and more with SC3 package. Click [here](sc3_ilc.html).

```{r, echo=FALSE, child="assets/session.Rmd"}
```

```{r, echo=FALSE, child="assets/build.Rmd"}
```

```{r, echo=FALSE, child="assets/footer.Rmd"}
```
